Pillar 2 - Topic Modeling

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
all transformations in one tibble

@@

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik) #this removes the degrees of freedom data
         )

@@

#Distributions
#NOTE: select how many topics to use

##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

extract_overview <- function() topic_model_gb %>% filter(n_topic == n_topics_overview)
extract_manual   <- function() topic_model_gb %>% filter(n_topic == n_topics_manual  )

df %>% mutate(var_new = list(var_old1, var_old2) %>% pmap(my_function))

data <- tribble(
  ~ ID,
  "overview",
  "manual"
  ) %>%
  mutate(df = if_else(ID == "overview", extract_overview(), extract_manual))

#Crop models
TM_overview <- topic_model_gb %>%
  filter(n_topic== n_topics_overview)

TM_manual   <- topic_model_gb %>%
  filter(n_topic== n_topics_manual)

#Distributions
distribution <- list()

distribution$beta$overview  <- TM_overview %>% pull(b_overview)
distribution$beta$manual    <- TM_manual   %>% pull(b_manual)

distribution$gamma$overview <- TM_overview %>% pull(g_overview)
distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)

```
##Inspect topics
```{r inspect topics, eval = FALSE}

# FUNCTION
#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
get_top_match <- function(d_distribution){
  print(!!sym(d_distribution))
}
Hi <- "hello"
get_top_match(Hi)

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term)) %>%
    select(top_words) %>%
    collapse(top_words)
}
#Saving to models
test_topic_model <-  test_topic_model %>%
  mutate(top_terms_topic = map(Beta, .f = get_top_terms_topic))

test_topic_model <- test_topic_model %>%
  mutate(top_topic_course = map(Gamma, .f = get_top_topics_course))

```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

go_down <- function(my_list, i){
  my_list[[i]]
}

get_key_words <-  function(d_top_words){

  select(top_words) %>%
    top_n(5)
}

View(test_topic_model)

a <- test_topic_model[["top_terms_topic"]]

d_top_words <- a[1]

#mutate(kw = get_key_words(top_terms_topic)) 
d_top_words <- a$top_terms_topic

kw <- lapply(
  distribution$beta,
  get_top_words
)

```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```

# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

@@

rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

>>>>

The following functions allow us to inspect the distributions and get kw
```{r}
# FUNCTION
#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}

# get_top_match <- function(d_distribution){
#   print(!!sym(d_distribution))
# }

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}

@@

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data

         #
         ##Inspect

         #top words per topic
         top_terms_topic = map(Beta, .f = get_top_terms_topic),

         #top topics per course
         top_topic_course = map(Gamma, .f = get_top_topics_course),

         #selecting keywords
         kw = map(Beta, .f = get_kw)
         )

@@

#App
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

@@

rm(a,b #,test)
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
